### 2017-03-30 paper/intro.tex
pass on intro section

At large organizations, the alternative of renting cloud
services\footnote{List of popular cloud services:
  \url{https://clutch.co/cloud}} or even building proprietary
infrastructures for running tests is a legitimate approach to mitigate
the regression testing problem.  However, for projects with low
budgets and yet relatively heavy testing workloads, this solution may
not be economically viable.  For these cases, the use of commodity
hardware, perhaps existing hardware, emerges as an attractive solution
for running tests.  The proliferation of multi-core CPUs and the
increasing popularization of testing frameworks with a rich support
for parallelization enables test suite speedups through increased CPU
usage~(see Section~\ref{sec:modes}).  This paper reports on an
empirical study we conducted to analyze the impact of low-level
parallelization to speedup testing in open-source projects.  This is a
relevant problem given the tremendous popularity of open-source
development and regression testing research.

The dimensions of analysis in this study are as follows.

\begin{itemize}
\item \textbf{Prevalence of long-running test suites.}
\item \textbf{Usage of test suite parallelization.}  
\item \textbf{Speedups of parallelization modes.}
\item \textbf{Issues with parallelization.}    
\end{itemize}

>>>>

At large organizations, the alternative of renting cloud
services\footnote{List of popular hosting cloud services:
  \url{https://clutch.co/cloud}} or even building proprietary
infrastructures to running tests is a legitimate approach to mitigate
the regression testing problem.  However, for projects with low
budgets and yet relatively heavy testing workloads, this solution may
not be economically viable.  For these cases, the use of commodity
hardware (\eg{}, existing workstations), emerges as an attractive
solution for running tests.  Furthermore, the proliferation of
multi-core CPUs and the increasing popularization of testing
frameworks and build systems, which today provide mature support for
parallelization, enable test execution speedups through increased CPU
usage~(see Section~\ref{sec:modes}).  These two elements~---~demand
for cost-effective test execution and supply of testing
infrastructure~---~led us to investigate if and how parallelization
features from testing frameworks and build systems are used in
practice.

This paper reports on an empirical study we conducted to analyze the
impact of low-level parallelization to speedup testing in open-source
projects.  This is a relevant problem given the tremendous popularity
of open-source development\Mar{Fan Long
  (http://people.csail.mit.edu/fanl/) often uses a plot to show the
  exponential rise of projects in github.  Please check if you can
  find a reference to that or ask Fan Long what source he used (maybe
  browsed with public API).} and regression testing
research~\cite{yoo-harman-stvr2012}.  The dimensions of analysis we
considered in this study are as follows.

\begin{enumerate}
\item \textbf{Prevalence of long-running test suites.}
\item \textbf{Usage of test suite parallelization.}  
\item \textbf{Speedups of parallelization.}
\item \textbf{Issues versus benefits on using parallelization modes.}
\end{enumerate}

Each dimension focuses on one aspect of our study.  The first
dimension measures to which extent open-source projects contain time
costly test suites.  In the limit, parallelization will be fruitless
if all project contain short-running test suites The second dimension
measures how often open-source projects, irrespective of their
associated testing costs, use parallelization schemes.  This dimension
is concerned with popularity of parallelization.  The third aspect
evaluates the observed impact of parallelization on cost.  Finally,
the last dimension evaluates the issues and benefits associated with
running test suites with different parallel configuration (/modes).
Overall, the study of these dimensions help us layout the current
state-of-the-practice in usage of parallelization in open-source
projects.

\Mar{organize according to each of these dimensions...$\rightarrow$}
